### 2014-10-21 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add TN number and bibtex entry

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

@@

\begingroup
\hypersetup{urlcolor=black}
This publication is available free of charge from:
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

@@

\begingroup
\hypersetup{urlcolor=black}
This publication is available free of charge from:
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

@@

August 2014}}

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (August 2014) \\
CODEN: NTNOEF}

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

>>>>

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note 1856}
\end{flushright}

@@

\begingroup
\hypersetup{urlcolor=black}
This publication is available free of charge from:
\href{http://dx.doi.org/10.6028/NIST.TN.1856}{http://dx.doi.org/10.6028/NIST.TN.1856}
\endgroup
}

@@

\begingroup
\hypersetup{urlcolor=black}
This publication is available free of charge from:
\href{http://dx.doi.org/10.6028/NIST.TN.1856}{http://dx.doi.org/10.6028/NIST.TN.1856} \\
\endgroup

@@

November 2014}}

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note 1856 \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~1856, \pageref{LastPage} pages (November 2014) \\
CODEN: NTNOEF}

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1856}{\bf http://dx.doi.org/10.6028/NIST.TN.1856} \\
\endgroup
